Bird beak's elaboration and exploration

### 2021-11-24 Analysis/02.1-shapespace_allbirds_lvl_superorder_order.Rmd
Update 02.1-shapespace_allbirds_lvl_superorder_order.Rmd

```{r, eval = TRUE}
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.MCMCglmm")
diagnose.mini.chains(shapespace_allbirds_lvl_superorder_order)
```

>>>>

```{r, eval = TRUE}
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.MCMCglmm")
diagnose.mini.chains(shapespace_allbirds_lvl_superorder_order[[1]])
```
